JLyrics \titlenote{Submitted as the final project for CS 410 Summer 2014.}

### 2014-08-01 report/paper.tex
Re-ordered report's merged sections.

@@

Piapro was a fairly simple site to crawl due to the site's structure. The pages were all indexed by number, which could be accessed via changing the URL itself. The first page could be accessed by this URL: ``http://piapro.jp/text/?categoryId=7\&page=1''. Changing the URL page number past the last page returns a page that says ``見つかりませんでした。'' or ``Couldn't find it.'' Each of these pages lists ten songs, for a grand total of just over 47,000 songs. These links are stored under ``http://piapro.jp/t/'' on the site itself. Each song has a unique id of four characters, such as ``KlF-'', which goes after the previous url. These pages contain the title, author, and lyrics data we needed.

>>>>

Piapro was a fairly simple site to crawl due to the site's structure. The pages were all indexed by number, which could be accessed via changing the URL itself. The first page could be accessed at \url{http://piapro.jp/text/?categoryId=7\&page=1}. Changing the URL page number past the last page returns a page that says ``見つかりませんでした。'' or ``Couldn't find it.'' Each of these pages lists ten songs, for a grand total of just over 47,000 songs. These links are stored under \url{http://piapro.jp/t/} on the site itself. Each song has a unique id of four characters, such as ``KlF-'', which goes after the previous url. These pages contain the title, author, and lyrics data we needed.

@@
